Life Expectancy

### 2024-06-08 products/manuscript/project-proposal.qmd
Proposal Commit

---
title: "Life Expectancy"
subtitle: "PArt 1: Project Proposal"
author: Sean O'Sullivan
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
---

>>>>

---
title: "Life Expectancy"
subtitle: "Part 1: Project Proposal"
author: Sean O'Sullivan
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
---
